---
title: "Hello R"
author: "Shikyna William"
date: "Data 2401"
output: 
  html_document: 
    fig_height: 7
    highlight: kate
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen dataset contains 1,846 rows and 3 columns.

There are 3 variables in this dataset are:

- dataset : indicates which dataset the data are from
- x : x-values
- y : y-values

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=5, fig.width=6}
dino_data <- datasaurus_dozen %>% 
  filter(dataset == "dino") 
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset:

```{r plot-star, fig.height=5, fig.width=6}
star_data <- datasaurus_dozen %>% 
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
### Comparison of "Star" dataset with "Dino" data set:
There is not much difference in the **correlation** value (both close to **0**) of the two data sets, however the shapes are drastically different.

- The `"dino"` dataset forms a **dinosaur shape**.
- The `"star"` dataset forms a **star shape**.

This highlights the importance of **visualizing data** rather than relying only on correlation coefficients.

### Exercise 4

First let's plot the data in the circle dataset:

```{r plot-circle, fig.height=6, fig.width=6}
circle_data <- datasaurus_dozen %>% 
  filter(dataset == "circle")
ggplot(data = circle_data, aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Comparison of "Circle" dataset with the "Dino" dataset:
As observed earlier, the correlation values for both datasets are close to 0, indicating little to no linear relationship. However, their shapes are drastically different:
- The "dino" dataset forms a **dinosaur shape**.
- The "circle" dataset forms a **circular pattern**, which inherently has no linear trend.

This reinforces the importance of **visualizing data** rather than relying solely on correlation coefficients, as different distributions can have the same summary statistics.

### Exercise 5
let’s plot all datasets at once and calculate their summary correlation coefficients.

```{r plot_all_datasets, fig.height=10, fig.width=10}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```



Finally, generating all the summary correlation coefficients:

```{r summary_corr}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
```

