---
title: "Hello R"
author: "Shikyna William"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen dataset contains 1,846 rows and 3 columns.

There are 3 variables in this dataset are:

- dataset : indicates which dataset the data are from
- x : x-values
- y : y-values

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>% 
  filter(dataset == "dino") 
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset:

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>% 
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
### **Comparison of "Star" dataset with "Dino" data set:**
There is not much difference in the **correlation** value (both close to **0**) of the two data sets, however the shapes are drastically different.

- The `"dino"` dataset forms a **dinosaur shape**.
- The `"star"` dataset forms a **star shape**.

This highlights the importance of **visualizing data** rather than relying only on correlation coefficients.

### Exercise 4

First let's plot the data in the circle dataset:

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>% 
  filter(dataset == "circle")
ggplot(data = circle_data, aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
### **Comparison of "Circle" dataset with the "Dino" dataset:**
As observed earlier, the correlation values for both datasets are close to 0, indicating little to no linear relationship. However, their shapes are drastically different:
- The "dino" dataset forms a **dinosaur shape**.
- The "circle" dataset forms a **circular pattern**, which inherently has no linear trend.

This reinforces the importance of **visualizing data** rather than relying solely on correlation coefficients, as different distributions can have the same summary statistics.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
